\papertitle

### 2012-10-13 manuscript.tex
Added Ryan's citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%TODO ryan
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is becominga well studied subject\cite{floreano:flying}. 
Shigeoka discusses velocity and altitude control in
~\cite{Shigeoka:ornithopter}. Design and control of the sub 15 gram DelFly
ornithopter is described by deCroon et al.~\cite{delfly:design}.
In contrast, there is little previous work on guidance of flapping wing 
MAVs. Baek demonstrated altitude control with an external 
camera~\cite{baek:altitude}. de Croon et al. demonstrated obstacle avoidance 
with an onboard camera and offboard processing~\cite{delfly:avoid}. For sub 20 gram
ornithopters, Baek et al. \cite{baek:tracking} is one of the few examples of
completely autonomous target seeking.
%[However, these papers do not study the system blah blah blah.]

Autonomous control of flapping winged MAVs is a complex undertaking because of
the non-linear flight dynamics as presented
in~\cite{humbert:dipteran2}\cite{cheng:tandrdamping}. Although the dynamics of
flapping-winged flight can be averaged with respect to the wingbeat period as
presented in~\cite{Schenato:flightcontrol}\cite{cheng:tandrdamping}, we develop a
linear, one-dimensional model to predict the behavior of the system, similar
to~\cite{Shigeoka:ornithopter}. In addition to the nonlinearities, the system
is underactuated due to size constraints. Many of the methods for controlling
these platforms make extensive use of GPS in outdoor
environments~\cite{kingston:timeattitude, kanade:3dvision} and expansive
motion capture systems in indoor environments. While operating indoors, using
GPS to estimate the pose of the MAV is not possible, and motion capture
requires expensive and stationary modification of the environment. The power
and payload limits on MAVs make on-board sensing difficult, so multi-agent
cooperative control schemes are apt solutions.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
%TODO ryan

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper}
% humphrey
In order to conduct these experiments on cooperation, we designed a new
flapping-wing MAV, known as the H$^2$Bird. Built around the Silverlit i-Bird 
RC flyer power train and clap-fling 
wings\footnote{\raggedright Silverlit Toys Manufactory Ltd.: i-Bird RC Flyer
\href{http://www.silverlit-flyingclub.com/wingsmaster/}
     {http://www.silverlit-flyingclub.com/wingsmaster/}}, 
the H$^2$Bird's wingspan is 26.5 cm and it has a flight weight of 13 grams. A 
tail propeller and servo-controlled tail elevator provide control in the yaw 
and pitch axes. The on-board ImageProc 2.4\footnote{ImageProc 2.4: \\
\href{https://github.com/biomimetics/imageproc\_pcb}
     {https://github.com/biomimetics/imageproc\_pcb}} 
electronics package consists of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed, and can operate for approximately 10 minutes.
%TODO footnote for ImageProc

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is becominga well studied subject\cite{floreano:flying}. 
Shigeoka discusses velocity and altitude control in
~\cite{Shigeoka:ornithopter}. Design and control of the sub 15 gram DelFly
ornithopter is described by deCroon et al.~\cite{delfly:design}.
In contrast, there is little previous work on guidance of flapping wing 
MAVs. Baek demonstrated altitude control with an external 
camera~\cite{baek:altitude}. de Croon et al. demonstrated obstacle avoidance 
with an onboard camera and offboard processing~\cite{delfly:avoid}. For sub 20 gram
ornithopters, Baek et al. \cite{baek:tracking} is one of the few examples of
completely autonomous target seeking.
%[However, these papers do not study the system blah blah blah.]

Autonomous control of flapping winged MAVs is a complex undertaking because of
the non-linear flight
dynamics~\cite{humbert:dipteran2}\cite{cheng:tandrdamping}. One approach to
simplify these dynamic models is to use averaging over the wingbeat
period~\cite{Schenato:flightcontrol}\cite{cheng:tandrdamping}. We desire a
simpler approach, so we develop a linear, one-dimensional model to predict the
yaw behavior of the system, similar to the model that Shigeoka used
in~\cite{Shigeoka:ornithopter} for simulating the velocity of a MAV in
one-dimensionally. In addition to the nonlinearities, the system is
underactuated (there is no roll control) due to size constraints.

Many of the methods for
controlling these platforms make extensive use of GPS in outdoor
environments and expansive
motion capture systems in indoor environments~\cite{kingston:timeattitude}\cite{kanade:3dvision}. While operating indoors, using
GPS to estimate the pose of the MAV is not possible, and motion capture
requires expensive and stationary modification of the environment. The power
and payload limits on MAVs make on-board sensing difficult, so multi-agent
cooperative control schemes are apt solutions.

@@

\cite{Jung1998Range}\cite{Hyams1999Cooperative}\cite{Mehta2006Adaptive}
\cite{Rudol2008Micro}\cite{Luo2011Air}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Robotic and Vision Platforms}
%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper}
% humphrey
In order to conduct these experiments on cooperation, we designed a new
flapping-wing MAV, known as the H$^2$Bird. Built around the Silverlit i-Bird 
RC flyer power train and clap-fling 
wings\footnote{\raggedright Silverlit Toys Manufactory Ltd.: i-Bird RC Flyer
\href{http://www.silverlit-flyingclub.com/wingsmaster/}
     {http://www.silverlit-flyingclub.com/wingsmaster/}}, 
the H$^2$Bird's wingspan is 26.5 cm and it has a flight weight of 13 grams. A 
tail propeller and servo-controlled tail elevator provide control in the yaw 
and pitch axes. The on-board ImageProc 2.4\footnote{ImageProc 2.4: \\
\href{https://github.com/biomimetics/imageproc\_pcb}
     {https://github.com/biomimetics/imageproc\_pcb}} 
electronics package consists of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed, and can operate for approximately 10 minutes.
%TODO footnote for ImageProc
